Tracing R Base: +

### 2019-05-05 notebooks/rplus.Rmd
some new stuff

] is somewhat interesting.
There were some issues with ].
The number of arguments that it takes is somewhat related to the dimensions of the thing being indexed.
For example, in data frames you can have a call to ] with 3 arguments: the data frame first, followed by the row and then column numbers (optionally).
For lists, it's always just 2 arguments.
Not sure how ... best to deal with this.
Right now, I just have it take 2 arguments: the thing being accessed, and an index variable.

There is perhaps room for a more sophisticateed analysis here, looking at the domensions of the first argument.
I don't think it'll be too challenging, but again, do we want to go that far?
I think that would be useful for some IDE tool or something: for instance, telling the programmer that they aren't using the thing with the right amount of dimensions.
Then again, you can totally do that and it's completely fine...

TODO: What package has the call with 1 argument?

>>>>

[ is somewhat interesting.
There were some issues with [.
The number of arguments that it takes is somewhat related to the dimensions of the thing being indexed.
For example, in data frames you can have a call to [ with 3 arguments: the data frame first, followed by the row and then column numbers (optionally).
For lists, it's always just 2 arguments.
Not sure how ... best to deal with this.
Right now, I just have it take 2 arguments: the thing being accessed, and an index variable.

There is perhaps room for a more sophisticateed analysis here, looking at the domensions of the first argument.
I don't think it'll be too challenging, but again, do we want to go that far?
I think that would be useful for some IDE tool or something: for instance, telling the programmer that they aren't using the thing with the right amount of dimensions.
Then again, you can totally do that and it's completely fine, you just might not get what you expect.

Cool:
src/main/names.c contains ~ function headers for builtin and special functions (minus types).
Notably, it includes the arity of the functions.
